Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-22 ms.tex
more details on 61-inch observing.

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
The nights were clear with the exception of a few passing clouds on 2016-07-14.
We also attempted photometry on 2016-06-10, but clouds prevented precision time series.
Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.

@@

All light curves are shown in Figure \ref{fig:allNightallStar}.
These are the same reference stars shown in Figure \ref{fig:refStars}.
The nights two nights 2016-06-12 and 2016-06-14 show greater overall stability than the ones in July, 2016.
We suspect that the higher moisture levels and occasional cloud passages (such as the ones that caused huge drops in flux on UT2016-07-14) affected the later observations.

>>>>

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory located on Mt Bigelow, Arizona on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
On all nights we used 90 second exposures using a Harris-R filter to best approximate the $r'$ filter used in \citet{schlawin2016kic1255}.
The nights were clear with the exception of a few passing clouds on 2016-07-14.
We also attempted photometry on 2016-06-10, but clouds prevented precision time series.
Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.
The data was taken in a 3x3 binning mode resulting in an effective 0.43"/pixel plate scale.
We used a photometric aperture of 9 pixels (3.9") and a background annulus from 9 to 12 pixels (3.9" to 5.2") on all stars and nights.

@@

All light curves for \shStar\ and the 12 reference stars are shown in Figure \ref{fig:allNightallStar}.
These are the same reference stars shown in Figure \ref{fig:refStars}.
The two nights 2016-06-12 and 2016-06-14 show greater overall stability than the ones in July, 2016.
We suspect that the higher moisture levels and occasional cloud passages (such as the ones that caused huge drops in flux on UT2016-07-14) affected the later observations.
